Cooling Requirements for the Vertical Shear Instability in Protoplanetary Disks

### 2015-05-03 appendix.tex
further refinements to appendix D2, D3. plus minor notation update

\subsection{Marginal stability for the fundamental
  mode}\label{bcrit_alt}
For the fundamental mode ($M=0$) we can deduce $\beta_c\ll 1$, which
motivates us to make this strong assumption from the onset. In this
case, Eq. \ref{relax_cond1} --- \ref{relax_cond2} 
imply the following balance for large $\khat$ and small
$\hat{\omega_c}$ while $\hat{\omega}_c\khat$ remain fixed:  
\begin{subequations}\begin{align}
    &0  = \left[1 + \gamma\beta_c^2\left(1-\gamma\right)\right] + 2h q
    \gamma \beta_c \left(\hat{\omega}_c\khat\right) - \left(\hat{\omega}_c\khat\right)^2,\\
    &0 =  \beta_c(1-\gamma) + hq \left(\hat{\omega}_c\khat\right). 
  \end{align}\end{subequations}
Then
\begin{align}
  \beta_c = \frac{h|q|}{\gamma-1}\left(1 - \frac{\gamma h^2 
      q^2}{\gamma-1}\right)^{-1/2},
\end{align}
which reduces to Eq. \ref{iso_vsi_cond} at $O(h)$.

>>>>

\subsection{Marginal stability for the fundamental
  mode}\label{bcrit_alt}
For the fundamental mode ($M=0$) we can deduce $\beta_c\ll 1$, which
motivates us to make this strong assumption from the onset. In this
case, Eq. \ref{relax_cond1} --- \ref{relax_cond2} 
imply the following balance for large $\khat$ and small
$\hat{\omega}_c$ while $\hat{\omega}_c\khat$ remain fixed:  
\begin{subequations}\begin{align}
    &0  = \left[1 + \gamma\beta_c^2\left(1-\gamma\right)\right] + 2h q
    \gamma \beta_c \left(\hat{\omega}_c\khat\right) - \left(\hat{\omega}_c\khat\right)^2,\\
    &0 =  \beta_c(1-\gamma) + hq \left(\hat{\omega}_c\khat\right). 
  \end{align}\end{subequations}
Then
\begin{align}
  \beta_c = \frac{h|q|}{\gamma-1}\left(1 - \frac{\gamma h^2 
      q^2}{\gamma-1}\right)^{-1/2},
\end{align}
which reduces to Eq. \ref{iso_vsi_cond} at $O(h)$.
